\documentclass[10pt,stdletter,dateno]{newlfm}
\usepackage{kpfonts}
\usepackage{url}

\usepackage{etoolbox}

\makeatletter
\patchcmd{\@zfancyhead}{\fancy@reset}{\f@nch@reset}{}{}
\patchcmd{\@set@em@up}{\f@ncyolh}{\f@nch@olh}{}{}
\patchcmd{\@set@em@up}{\f@ncyolh}{\f@nch@olh}{}{}
\patchcmd{\@set@em@up}{\f@ncyorh}{\f@nch@orh}{}{}
\makeatother

\widowpenalty=500
\clubpenalty=500

\newlfmP{headermarginskip=-10pt}
\newlfmP{sigsize=10pt}
\newlfmP{dateskipafter=5pt}
\newlfmP{addrfromphone}
\newlfmP{addrfromemail}
\PhrPhone{Phone}
\PhrEmail{Email}

\namefrom{Kenneth Long}
\addrfrom{%
    \today\\[5pt]
    Kenneth Long \\
    Route de Champvigny 51 \\
    1242 Satigny, Switzerland
}
\phonefrom{+41 77 503 9513}
\emailfrom{kdlong07@gmail.com}

\addrto{%
Expedia Group\\
Geneva, Switzerland}

\greetto{Dear Hiring Manager,}
\closeline{With best regards,}
\begin{document}
\begin{newlfm}

I was thrilled to see your job announcement for a Data Scientist position at Expedia Group. 
I am very familiar with the huge range of tools that Expedia has developed to help consumers feel confident while
finding flexible and affordable travel solutions.
With more than five years of experience as a researcher and data scientist working on the analysis of petabytes of data 
collected at CERN in Geneva, Switzerland, I am passionate about using data to build
complex insights and to drive results.
I am eager to bring the forward-thinking approach
that I developed while working at one of the most innovative scientific laboratories in the world to a company
that harnesses the power of data to make travel accessible, affordable, and comfortable for all.
I know that Expedia Group shares my passion for innovative solutions, and I am confident that I would be
an asset to the thriving data science team at Expedia Group in Geneva.

\textbf{What specifically could I bring to your team?}

\begin{itemize}
    \item \textbf{An innovative and results-oriented mindset}

    I have coordinated diverse groups of colleagues in novel data-analysis projects,
    from estimating properties of data sets with complex maximum likelihood fits to exploring new methods of clustering 
    with graph neural networks.

    \item \textbf{Expertise in data science analysis and visualization tools}  

    I am experienced in Python, R, and Scala and their analysis, machine learning,  and visualization packages,
    including TensorFlow, Keras, Matplotlib, Plotly, and ggplot.
    I have studied and used many other programming languages, making me comfortable and adept at learning new tools quickly.

    \item \textbf{Excellent communication and presentation skills}
        
    I am skilled at preparing technical reports and communicating complex ideas to a variety of audiences. 
    I have presented scientific research at tens of international conferences and have lead seminars and science outreach efforts for the general public.

\end{itemize}

Finally, my strong work ethic and ability to build relationships with people from all cultures has allowed me to
be a leader in a cutting-edge scientific environment for the past seven years. I am interested in bringing this
approach to a consumer-oriented business, and I am confident that the team at Expedia Group is a great match for my skills and interests.


I would be delighted to further discuss the value I could bring to your team. Thank you very much 
for your consideration, and I look forward to hearing from you.
\end{newlfm}
\end{document}
